\CVSection{Hobby projects}
\CVItem{Home automation} \\
\emph{Topics: Micro-services, Go, Python, C, C++, Flutter, Javascript, Docker, Kuberneters, CI/CD, Kafka, GCP, HTTP, Embedded, Electronics, Wireless, Sensor-network, Google-home assistant, Monitoring} \\
\SmallSep
My biggest and longest running private project, I started the project in 2020 abd work on it in my spare time. The project is used to learn new languages, software engineering concepts, patterns, practice running long projects and most of all for fun. \\
\VerySmallSep
The project is running in my home, monitoring the house and garden, as well as giving some control prosibility to my family. All the source code is publicly avaible on my Github page (www.github.com/dankersw) \\
\VerySmallSep
Currently of writing, the system includes:
\begin{compactitem}[\color{RoyalBlue}$\circ$]
    \item A battery powered wireless sensor network that receives information (temperature, humidity, soil humidity (plants), light, air quality, door and window status, etc) and saves it for monitoring and visualization. This includes custom make micro-controlers and gateway electronics design.
    \item A PoC which makes it possible to voice contol the system using my Google home-assistant enabled internet speakers.
    \item CI/CD pipelines that deploys the updates micro-services automatically to my Kubernetes cluster.
    \item Web page for monitoring the house.
    \item A Flutter based smart-mirror that shows the departure times of the nearst busses and trams, the families todo list, predicted and current weather, etc.
    \item A system to create and automate different scenes using lighting and blinds
\end{compactitem}
\Sep

\CVItem{Portfolio website} \\
Like any engineer interested in software, did I make a small and simple portfolio website. The website is writen in Typescript using the React framework. Before this project I never made any non text-based GUI.\\
The source code is availible on my Github page and is hosted on the URL dankersw.github.io
\Sep

\CVItem{DIY drone} \\
\emph{Topics: Robotics, Wireless communication, Python, Gyroscope} \\
Powerful lifting drone that was completely build from scratch including the remote controller, stabilisation algorithm and control software.
\Sep

\CVItem{Woodworking projects} \\
In my spare time I like to build and thinker. At home I have made several wooden funitures and build-ins where design and functionolity is one of the main key-points. This is done to the maximase the availible space to the fullest. I desing the pieces using 3D modeling software (sketch-up) \\
Some project I made are a storage bed, coffee-table, outdoor furniture, building closets, bench, and store shelfs
\Sep
