\CVSection{Work portfolio}

\CVItem{Vinnter}

\SmallSep
\textbf{LTE cloud connector firmware application:} Build and designed a cloud connector application running on 300 devices as part of trail project. I handled both the embedded firmware as well as the cloud configuration. On the cloud side (AWS) I wrote a custom fleet-provisioning service stack using CDK (Python) to safely and automatically onboard the devices into AWS as well as some custom serverless functions to handle device communication, firmware updates, and device management. On the device side, I was writing firmware for the NRF9160 SiP using the Zephyr RTOS (C). The application handled cloud communication using LTE-M, Firmware over the air (FOTA) upgrades, and certificate rotation. One of the hardest parts was battery management because the radio had to be on all the time and the system was running on batteries. I also architected the system design for the other parts that interact with sensors and mechanical components.  
\SmallSep

\textbf{Custom Debian based OS image:} In-house project that started 15 years earlier and wasn't touched for 10 years. As part of the new facelift, I worked on compiling the legacy code (C++) for new hardware, moved the build infrastructure (handful of huge shell scripts) from a dying laptop into the cloud, integrated into a CI, packaged all services into debian packages from the CI, setup service management (systemd), and created a custom Debian OS image. All done via Gitlab CI pipelines.
\SmallSep

\textbf{Welding system IoT Gateway:} Consultant at Esab. Maintaining and developing Linux based gateway application with a microservices architecture running on a Single-board computer, the micro-services communicate using gRPC. Languages of the services ranged from Go, C++, Python, and JS (Vue). The gateway is part of a bigger system and communicates with other nodes in the system via HTTP. I created and maintained serval applications and services, all the services I created were written in Go. Our architecture supported different (gateway) platforms/hardware as well as different welding systems and configurations.
\SmallSep 

\textbf{Radar presence detection:} Small PoC project to verify if a radar system could be used to track the usage of a welding booth. The radar system and detection algorithms were provided by a supplier. My task included creating webhooks for our clouds to communicate as well as a monitoring tool to visualize the received data. 
\SmallSep

\textbf{BLE Sensor network firmware development:} Worked on an in-house project where we build a wireless thermostat system for floor heating. The product was FULLY developed In-house ranging from electronics and plastics to software. I joined the project at a later stage. My main contributions to the project were that I developed a HIL and SIL (Hardware and Software in the Loop) system to run big system tests on multiple targets (communicating wirelessly with each other) as well as performance tests on single targets. Some custom hardware was also developed to achieve this goal. The tests were automatically triggered via CI/CD pipelines. \\ 
\Sep

\CVItem{Volvo Group}

\SmallSep
\textbf{Verification platform:} Redesigned how Bitbucket events trigger Jenkins jobs, and how the CI-CD chain is build-up. Kafka was used as message queue between several created Dockerized micro services written in Python that were spread out over the Volvo network. I designed the system from a conceptional idea to a production ready implementation. The project is used by the verification department of the Connectivity Group.
\SmallSep

\textbf{DevOps Engineer:} Created and maintained several CI-CD freestyle Jenkins jobs (Python) as part of the CI team responsible for the telematics gateway.
\SmallSep

\textbf{Data logging system:} Prototyped and developed (C++) a data logging system for autonomous and concept vehicles. Including hardware selection, embedded software, design of an on- and offboard QUI, data storage, as well as remote controlling of the logging unit. 
\SmallSep

\textbf{Scrum master:} Scrum master on the agile release train that created the first commercial autonomous transportation solution.
\SmallSep

\textbf{Communication infrastructure to enable autonomous driving:} Investigating the requirements, selection of Hardware and technologies, as well as on-site measurements. Later on I became the element owner of the wireless communication infrastructure at the project's customer.  
\SmallSep

\textbf{Research projects:} Software Developer (C++) on public funded research projects with a focus on C-ITS. \\
\Sep

\CVItem{Memory x design} \\
Prototyped the next phase of the customers product road-map.